\documentclass[margin,line]{res}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=blue,filecolor=magenta,urlcolor=cyan}
\evensidemargin -.3in
\oddsidemargin -.3in
\itemsep=0in
\parsep=0in
\textwidth=5.5in
\textheight=720pt
 
\urlstyle{same}

\begin{document}
\name{Filip Jeremic \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}

\vspace{.05in}

\begin{tabular}{@{}p{3.36in}p{3in}}
\href{mailto:filip@jeremic.ca}{\texttt{filip@jeremic.ca}} & \href{https://jeremic.ca}{\texttt{https://jeremic.ca}} \\
& \href{https://github.com/fjeremic}{\texttt{https://github.com/fjeremic}}
\end{tabular}

\section{\sc Interests}

Compiler development (static and dynamic), programming languages (design and implementation), machine learning, data
science, parallelization, computer graphics, software protection, reverse engineering, and malware analysis.

\section{\sc Technical \newline Skills}

{\bf C, C++, Python, x86-64 Assembly, C\#, Java} \\
{\em Expert, 10+ years}

These technologies are the ones which I have used the most over the years. Because of my field of interest, low level
programming languages such as various flavors of assembly, C, and C++ have been my primary languages of choice. Working 
on a just-in-time (JIT) compiler for Java has made me deeply familiar with these languages both from the angle of 
software engineering and performance optimization.

{\bf Linux, Unix tools, Windows } \\
{\em Advanced, 8+ years}

My primary development platforms is Linux. I am very comfortable within a Unix environment carrying out tasks such as
instruction level performance investigations (perf), assembly or source level debugging (gdb, IDA, Ollydgb, etc.), and
remote SSH development using the technologies listed above.

{\bf Docker, Jenkins, CMake, Bash, Qt, JavaScript, Perl, HTML, WPF, UWP } \\
{\em Experienced, 7+ years}

\section{\sc Professional Experience}
{\bf IBM}, Toronto, Canada

{\em Compiler development - Advisory Software Engineer} \hfill {\bf 2017 - Present}
\vspace{-.12in}

A natural progression of my previous position into a team leadership role within the backend area of the JIT compiler 
technology I had been working on for several years. During this exciting time we worked on open sourcing our compiler
technology as part of the \href{https://github.com/eclipse/openj9}{Eclipse OpenJ9} and 
\href{https://github.com/eclipse/omr}{Eclipse OMR} projects at GitHub. As the open source communities grew, my role has
been evolving into being one of the focal points for cross-platform backend JIT development and community management
within the realms of my expertise. I am currently the top code \href{https://github.com/eclipse/omr/graphs/contributors}
{contributor} across both projects as per the GitHub statistics and I am heavily involved in 
\href{https://github.com/eclipse/omr/pulls?q=is%3Apr+sort%3Aupdated-desc+reviewed-by%3Afjeremic+is%3Aclosed+}{reviewing} 
contributions to both projects.

{\em Compiler development - Staff Software Engineer} \hfill {\bf 2015 - 2017}
\vspace{-.12in}

An extension of my previous role with a broader focus primarily on performance acceleration of Java workloads on Linux
and z/OS. Among development items this role involved instruction level profiling of Java applications and identifying
bottlenecks which can be optimized in the JIT compiler. The performance investigation is done at an instruction level
but common intermediate language (IL) level optimizations were developed as part of the experimentation such that all
supported backends (x86, Power, z/Architecture, ARM, AArch64, RISC-V) can benefit.

\newpage

Part of my role also involved sharing the burden of some of the team leads responsibilities in technical management of
work items triaged to the rest of the development team, and the delivery of performance improvement targets for the
release of Java 9.

{\em Compiler development - Associate Software Engineer} \hfill {\bf 2013 - 2015}
\vspace{-.12in}

Directly after graduation I took a position at IBM Canada's compiler group where I worked on the backend of the
just-in-time (JIT) compiler for the IBM J9 Java Virtual Machine (JVM) in support of IBM platforms.

\vspace{.10in}

\begin{itemize}
\item Worked on a team developing the backend code generator for z/Architecture based processors
\begin{itemize}
\item Designed and developed various compiler features ranging from intrinsics libraries, register allocation,
instruction scheduling, and optimal instruction selection for the target processor
\item Carried out instruction level performance investigations on various workloads and implemented changes to
the backend code generator to realize the performance gains
\item Postmortem core dump analysis of non-deterministic code generator bugs
\end{itemize}
\item Developed a firm understanding the interaction between the various components of a dynamic runtime 
environment (VM, GC, JIT), particularly in the context of a JVM
\end{itemize}

\section{\sc Patents}

\begin{list}{\labelitemi}{\leftmargin=0cm}

\item {\em \bf Object load introspection using guarded storage}

\href{https://patents.google.com/patent/US11080182B2}{Patent No. US11080182B2} \hfill {\bf Issued 2021-08-03}

\item {\em \bf Software-directed value profiling with hardware-based guarded storage facility}

\href{https://patents.google.com/patent/US20210208927A1}{Patent No. US20210208927A1} \hfill {\bf Issued 2021-07-08}

\item {\em \bf Copying and forwarding for concurrent copying garbage collection}

\href{https://patents.google.com/patent/US10877884B2}{Patent No. US10877884B2} \hfill {\bf Issued 2020-12-29}

\item {\em \bf Multi-byte compressed string representation}

\href{https://patents.google.com/patent/US10002010B2}{Patent No. US10002010B2} \hfill {\bf Issued 2018-06-19}

\end{list}

\section{\sc Education}

{\bf McMaster University}, Hamilton, Ontario, Canada

\vspace{-.3cm}

{\em Master's Student} \hfill {\bf 2012 - 2013}

\vspace{-.4cm}

M.Eng., Computer Science

{\bf McMaster University}, Hamilton, Ontario, Canada

\vspace{-.3cm}

{\em Undergraduate Student} \hfill {\bf 2008 - 2012}

\vspace{-.4cm}

B.Sc., Honours Mathematics and Computer Science

\begin{center}
\textbf{References available upon request.}
\end{center}

\end{resume}
\end{document}
